% !TEX program = lualatex
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
% Adapted for LuaLaTeX
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor} % Switched to xcolor for better color management
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontspec} % Use fontspec for font selection with LuaLaTeX

%----------FONT OPTIONS----------
% With LuaLaTeX, you can use any font installed on your system (or available in Overleaf).
% Examples:
% \setmainfont{Fira Sans}
% \setmainfont{Roboto}
% \setmainfont{Source Sans Pro}
% \setmainfont{Charter}
% \setmainfont{Cormorant Garamond}
%----------FONT OPTIONS----------
\setmainfont{Inter-Regular.ttf}[
  Path = ./fonts/,
  BoldFont = Inter-Bold.ttf,
  ItalicFont = Inter-Italic.ttf,
  BoldItalicFont = Inter-BoldItalic.ttf
]


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge  Dhanwanth Parameswar} \\ \vspace{1pt}
    \small \href{tel:+17342692684}{\underline{734-269-2684}} $|$ \href{mailto:im@dhanwanth.com}{\underline{im@dhanwanth.com}} $|$ 
    \href{https://linkedin.com/in/dhanwanthp}{\underline{linkedin.com/in/dhanwanthp}} $|$
    \href{https://github.com/DhanwanthParameswar}{\underline{github.com/dhanwanthparameswar}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University at Buffalo}{Buffalo, NY}
      {Bachelor of Science in Computer Engineering, Honors College Scholar}{Expected May 2028}
        \resumeItemListStart
        \resumeItem{Relevant Coursework: Intro to Computer Science II (CSE 116), Intro to Discrete Structures (CSE 191)}
      \resumeItemListEnd
    % \resumeSubheading
    %   {Pittsford Mendon High School}{Pittsford, NY}
    %   {High Honor Roll, NHS, AP Scholar with Distinction}{June 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Audio Plugin Developer}{April 2023 -- Present}
      {NEST Acoustics}{}
      \resumeItemListStart
        \resumeItem{Engineering VST audio plugin software using HISE/JUCE for a virtual instrument company, enabling users to play and manipulate audio samples.}
        \resumeItem{Collaborated with the founder to define product specifications and user interface requirements.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Intern - AI/Machine Learning}{May 2024 -- October 2024}
      {Rochester Institute of Technology}{Rochester, NY}
      \resumeItemListStart
        \resumeItem{Worked under the guidance of Professor Haibo Yang to explore federated learning networks and practical AI applications.}
        \resumeItem{Developed an in-browser AI image classifier using TensorFlow.js, leveraging a MobileNetV3 base model with a custom head trained on the Caltech 256 dataset.}
        \resumeItem{Engineered the user interface with React and Tailwind CSS, utilizing the Filepond library for robust image input.}
      \resumeItemListEnd

    \resumeSubheading
      {Swim Instructor/Lifeguard}{March 2024 -- June 2025}
      {YMCA of Rochester}{Pittsford, NY}
      \resumeItemListStart
        \resumeItem{Ensured safety for dozens of swimmers in a high-traffic pool environment while instructing children in fundamental and competitive swimming techniques.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Library Management System} $|$ \emph{PHP, JavaScript, MySQL, HTML, CSS}}{September 2023 -- May 2024}
            \resumeItemListStart
              \resumeItem{Engineered a full-stack web application to digitize a physical inventory of 1,000+ volumes, serving a community of $\sim$150 members.}
              \resumeItem{Reduced book return processing time by $\sim$95\% (from 5 mins to $<$15 seconds) by implementing indexed database queries to replace manual logbook searching.}
              \resumeItem{Streamlined asset tracking for 200+ loan transactions, eliminating manual clerical errors and ensuring data integrity for lost item tracking.}
            \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Droppua} $|$ \emph{JavaScript, PHP, Docker, MySQL}}{June 2024 -- July 2024}
          \resumeItemListStart
            \resumeItem{Engineered a real-time web application for seamless text and file sharing across devices without page reloads.}
            \resumeItem{Utilized Server-Sent Events (SSE) with a PHP backend to efficiently stream data from a MySQL database to the client.}
            \resumeItem{Designed an intuitive user interface and developed an iOS Shortcut integration to maximize ease of use.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Non-Profit Website} $|$ \emph{WordPress}}{July 2023 -- September 2023}
          \resumeItemListStart
            \resumeItem{Developed and deployed a public-facing WordPress site for GramNY, a local nonprofit, to enhance their online presence and attract new members.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, PHP, SQL, JavaScript/TypeScript, HTML/CSS} \\
     \textbf{Technologies}{: React, Tailwind CSS, Node.js, TensorFlow.js, HISE/JUCE, WordPress, Git, Docker, OCI, GCP}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}